A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-19 manuscript.Rmd
move sections around

These function again should be accept the output of `planned_analysis()` as input.
Ideally, these three functions can be composed to create a "fake" results section, e.g. when composed to `report_analysis(planned_analysis(simulate_data()))` or `simulate_data() %>% planned_analysis() %>% report_analysis()` outputs a results section formatted in Markdown.

>>>>

These function again should be accept the output of `planned_analysis()` as input.
The output of this function should be formatted in Markdown.
A variety of packages automatically generate well formatted outputs of statistical reports or even entire tables of estimates or figures directly from R objects.
Packages like [`pander`](https://github.com/Rapporter/pander) [@pander], [`stargazer`](https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf) [@stargazer], [`apaTables`](https://dstanley4.github.io/apaTables/articles/apaTables.html) [@apaTables] and [`papaja`](http://frederikaust.com/papaja_man/) [@papaja] help you to create dynamically generated professional looking results.
The package [`report`](https://github.com/easystats/report) [@report] is particularly noteworthy because it not only generates tables, but also a simple interpretation of the effects as actual prose (e.g it quantifies the size of an effect).

Ideally, these three functions can be composed to create a "fake" results section, e.g. when composed to `report_analysis(planned_analysis(simulate_data()))` or `simulate_data() %>% planned_analysis() %>% report_analysis()` outputs a results section.

To summarize researchers write three functions, `planned_analysis()`, `simulate_data()`, and `report_analysis()` and embed these into a manuscript that serves as preregistration.
After they gathered the actual data, they replace the simulated data, run `planned_analysis()` and write the discussion.
